|

### 2024-03-15 examples/_1a_Examples_DifferenceScores_PairedTtests.qmd
manuscript updates

:::

@@

knitr::opts_chunk$set(
    echo = T, message = F, warning = F, error = F,
    comment = NA, cache = T, code_folding = T,
    R.options = list(width = 220, digits = 3),
    fig.align = "center",
    out.width = "75%", fig.asp = .75
)
```

:::

@@

```{r}
# Install and load the googledrive package
if (!requireNamespace("googledrive", quietly = TRUE)) install.packages("googledrive")
library(googledrive)

# Authenticate with Google Drive
drive_auth()

# Specify the file ID and the destination path
file_id <- "1_gnaEx0wJ28tT0CD_B6mPFwngdfSb6Dr" # Replace with your actual file ID
dest_file <- "my_data.rds" # Specify your destination path

# Download the file
drive_download(as_id(file_id), path = dest_file, overwrite = TRUE)

# Load the .rds file for analysis
my_data <- readRDS(dest_file)

# Begin your analysis (example: view the first few rows)
head(my_data)

:::

<!-- ::: blue
**This code reads in and shows the data to be used in the current
example** -->

<!-- ```{r read-data}
#| echo: TRUE
#| messages: FALSE
#| warning: FALSE
#| output: FALSE
#| cache: FALSE

@@

# Define event names to be retained in the analysis and convert variables to appropriate data types
eventnames_to_include <- c("baseline_year_1_arm_1",
                           "1_year_follow_up_y_arm_1",
                           "2_year_follow_up_y_arm_1",
                           "3_year_follow_up_y_arm_1",
                           "4_year_follow_up_y_arm_1")

@@

```
::: -->

----

<!-- ```{r}
# Install and load the googledrive package
if (!requireNamespace("googledrive", quietly = TRUE)) install.packages("googledrive")
library(googledrive)

# Authenticate with Google Drive

# Specify the file ID and the destination path
file_id <- "1_gnaEx0wJ28tT0CD_B6mPFwngdfSb6Dr" # Replace with your actual file ID
dest_file <- "my_data.rds" # Specify your destination path

# Download the file
drive_download(as_id(file_id), path = dest_file, overwrite = TRUE)

# Load the .rds file for analysis
my_data <- readRDS(dest_file)

# Begin your analysis (example: view the first few rows)
head(my_data)

``` -->

```{r}
# Set the URL for the CSV file
file_url <- "https://drive.google.com/file/d/1_gnaEx0wJ28tT0CD_B6mPFwngdfSb6Dr/view?usp=drive_link"

# Set the destination filename
dest_file <- "my_data.rds"

# Download the file
download.file(file_url, destfile = dest_file, mode = "wb")

# Read the CSV file into R
my_data <- readRDS(dest_file)

# Display the first few rows of the data
head(my_data)
```

----

>>>>

```
:::

@@

knitr::opts_chunk$set(
    echo = T, message = F, warning = F, error = F,
    comment = NA, cache = T, code_folding = T,
    R.options = list(width = 220, digits = 3),
    fig.align = "center",
    out.width = "75%", fig.asp = .75
)
```
:::
:::

@@

::: blue

**This code reads in and shows the data to be used in the current example**

```{r read-data}
#| echo: TRUE
#| messages: FALSE
#| warning: FALSE
#| output: FALSE
#| cache: FALSE

@@

# Define event names to be retained in the analysis and convert variables to appropriate data types
eventnames_to_include <- c(
    "baseline_year_1_arm_1",
    "1_year_follow_up_y_arm_1",
    "2_year_follow_up_y_arm_1",
    "3_year_follow_up_y_arm_1",
    "4_year_follow_up_y_arm_1"
)

@@

```
:::

### 2024-03-15 examples/_queue/_4_Examples_SignedRankTest.qmd
manuscript updates

::: blue
**This code reads in and shows the data to be used in the current
example**

@@

**Descriptive Statistics for the Signed Rank Test result**
```{r model-output}
#| echo: TRUE
#| messages: FALSE
#| warning: FALSE
#| code-summary: testing

library(gridExtra)

# Creating the first density plot with ggplot2
p1 <- ggplot(data.frame(x = na.omit(df_wide$income_numeric_0)), aes(x = x)) +
  geom_density(fill="red", color="blue") +
  labs(title = "Kernel Density of Income at Baseline")

# Creating the second density plot with ggplot2
p2 <- ggplot(data.frame(x = na.omit(df_wide$income_numeric_1)), aes(x = x)) +
  geom_density(fill="blue", color="red") +
  labs(title = "Kernel Density of Income at T1")

p3<- ggplot(df_wide, aes(x = income_numeric_0, y = income_numeric_1)) + geom_point(color="#04c24a")

# Create both plot and store in variable
p4<-ggplot(df_wide, aes(x=income_numeric_0, y=income_numeric_1))+
geom_segment( aes(x=income_numeric_0, xend=income_numeric_1, y=0, yend=income_numeric_2), color="grey") + geom_point( color="green", size=4)

p5<-ggplot(df_wide, aes(x = income_numeric_0)) + 
geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)

p6<-ggplot(df_wide, aes(x=income_numeric_0, y=income_numeric_1)) + 
geom_bar(fill="#69b3a2", stat = "identity")

# Arrange the ggplot2 objects on a grid
grid.arrange(p1, p2, p3, p4, p5, p6, ncol = 3)

ggplot(df_wide, aes(x = sex, y = income_numeric_0, fill = sex)) +
  geom_boxplot() +
  scale_fill_manual(values = c("orange", "darkgrey")) +
  theme_bw() +
  theme(legend.position = "none")
```

This signed rank test evaluates xxxx. The model output provides:

i. xxxxx;
ii. xxxxx;
iii. xxxxx;
iv. xxxxx;
v. xxxxx.

With a xxxx of `xxxxx` and a p-value of `xxxxx`, we can xxxx. Furthermore, we can xxx that xxxxx. This indicates xxxxxx in weight from Baseline to Year 1.

>>>>

**This code reads in and shows the data to be used in the current example**

@@

### 2024-03-15 manuscript/manuscript.qmd
manuscript updates

[!Longitudinal Models/Data Structures](img/Mindmap1copy.png)]{#fig-LONGmod fig-alt="Longitudinal Models Diagram." width="300" height="300" fig-align="left"}

>>>>

[!Longitudinal Models/Data Structures](img/Mindmap1copy.png){#fig-LONGmod fig-alt="Longitudinal Models Diagram." width="300" height="300" fig-align="left"}
